\subsubsection{ResNext}
Source: \parencite{kone2018hierarchical}
\newline
Article title: Hierarchical ResNeXt Models for Breast Cancer Histology Image Classification
\newline
Tags: [ResNext], [CNN], [CL]
\newline
Description:
\newline
The article is using BACH system challenge for image classification. With that, they are trying to predict the stage of breast cancer. With the train/test split of 75/25, the accuracy they are getting with ResNext is 0.99.
\newline

Source: \parencite{sharma2018spatial}
\newline
Article title: Spatial Image Steganalysis Based on ResNeXt 
\newline
Tags: [ResNext], [CNN], [CL]
\newline
Description:
\newline
This article is an example of great use of ResNeXt. They are using CNN on ResNext to generate stronger image representations for steganalysis. With this they can easily detect hidden secret messages within images (steganalysis).
\newline

Source: \parencite{orhan2019robustness}
\newline
Article title: Robustness properties of Facebook's ResNeXt WSL models 
\newline
Tags: [ResNext]
Description:
\newline
Facebook (now known as Meta) has published Facebook AI which is trained on ~1B images from Instagram. Researchers in this article have compared the model with the ResNext and tried its robustness.
\newline

Source: \parencite{pant2020resnext}
\newline
Article title: ResNeXt convolution neural network topology-based deep learning model for identification and classification of Pediastrum
\newline
Tags: [ResNext], [CNN]
\newline
Description:
\newline
This article is describing use of ResNext model on data set of 42k images. ResNext topology differentiates cells based on information in the data and gives the experimental result of 98.45percent and F1 score of 98. Since ResNext is a contender for algorithms, this is an amazing discovery.